A Detection of the Environmental Dependence of the Stellar Profiles and haloes of Massive Central Galaxies

### 2017-07-13 draft/paper2.tex
Edit results 3

\title[Structure and Environment of Massive Galaxies]{
       A Detection of the Environmental Dependence of the Stellar Profiles and Halos
       of Massive Central Galaxies}

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    For the first time, we conclusively show that at fixed stellar mass, massive central 
    galaxies display mass density profiles that are not self similar and which 
    present subtle but systematic differences that correlate with \mhalo{}. 
    On average, massive central galaxies in more massive halos have shallower inner 
    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
    envelopes. 
    These differences translate into a clear environmental dependence of the mass-size 
    relation: central galaxies in more massive halos have larger $R_{\mathrm{50}}$ 
    at fixed \mtot{}. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    Furthermore, because galaxies in larger halos have more extended envelopes, 
    the amount of light that is missed will be halo mass dependent. 
    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
    in the amplitude of stellar profiles at 100 kpc. 
    We argue that ``cD'' galaxies represent the tail end of a distribution and 
    are not a distinct class of massive galaxies. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation. 
    \song{This is the abstract of old draft, need some works}

@@

    According to this two-phase formation scenario, the late time growth of massive 
    ETGs is intrinsically tied to the growth of their host dark matter halos 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive halos should experience 
    different assembly and should be subject to higher merger rate compared to 
    ETGs with similar \mstar{} that live in less massive dark matter halos. 
    A natural prediction of this picture is therefore that the structures of 
    massive ETGs should depend on their ``environment''\footnote{There are 
    different definitions of ``environment'' in the literature.  
    In this work, we use ``environment'' and halo mass interchangeably.}.
    For instance, models based on two-phase scenario predict that the well-know 
    stellar mass--effective radius relation for ETGs (\mstar{}--$R_{\rm e}$ relation; 
    e.g., \citealt{Shen2003, Guo2009}) should show environmental dependence: the 
    $R_{\rm e}$ of massive ETGs in more massive halos should be larger than those 
    in less massive halos at fixed \mstar{} 
    (e.g. \citealt{Shankar2013, Shankar2014}).
    Yet, solid evidence of this effect at low redshift is still missing 
    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).

@@

    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that the deep, 
    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} massive galaxies 
    at $0.3 < z < 0.5$ out to 100 kpc. 
    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
    and the shapes of the stellar halos of massive ETGs has a clear \mstar{} 
    dependence. 
    And the fraction of accreted stars residing in the extended envelope increases
    with the total \mstar{} of the galaxy.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          The left panel corresponds to samples matched by ``total'' stellar mass 
          (\mtot{}). 
          The right panel corresponds to samples matched by ``core-mass'' (\minn{}). 
          Orange and red lines correspond to central galaxies living in halos with 
          \logmh{} $\geq 14.2$. 
          Black and grey correspond to central galaxies living in halos with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          The brown line in the bottom panels show the relative difference between 
          two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}})$). 
          Errors on the difference between the two profiles is computed via bootstrap 
          too. 
          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial signal. 
          We repeat this process 5000 times.  
          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We also wish to focus on massive galaxies that live at the centers of their own 
    dark matter halos-- so-called ``central'' galaxies.  
    They are uniquely important to the study of galaxy-halo connection and are known 
    to follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
    Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{} end with small scatter.
    We utilize the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
    to identify central galaxies.

    Firstly, we select 68 massive central galaxies from the \redm{} clusters 
    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness of low richness clusters
    at the high end of our redshift window, and the $P_{\mathrm{Cen}}$ limit is 
    selected to exclude low probability candidate of central galaxy. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
    galaxies are the brightest cluster galaxies (BCGs) of clusters with 
    \mhalo{}$>10^{14.2}$~\msun{}.
    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in more massive halos} as 
    the \rbcg{} sample.

    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
    \citet{Simet2016}. 
    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
    \citet{Diemer2015}. 
    And we exclude all galaxies within a cylinder around each cluster, with the radius
    equal to $R_{\mathrm{200b}}$ and length equal to twice the value of the photometric 
    redshift uncertainty (typically around 0.015 to 0.025). 
    We generally consider this sample as the central galaxies living in halos with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}.
    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
    $0.3 < z < 0.5$. 
    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6). 
    Satellite contamination should be relative low at the high-\mtot{} end
    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
    For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
    contamination in the \logmtot{}$>11.6$ sample from satellites from 
    \logmh$<11.4$ haloes.

@@

    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies show 
    intriguing diversity on the \mtot{}-\minn{} plane and in their \mden{} profiles 
    in the outer haloes.  
    In Paper~1, we explore the \mstar{}-dependence of the stellar halos in massive 
    galaxies, and conclude that the general trends are consistent with the 
    predictions of two-phase formation scenario. 
    In the following sections, we will investigate the relation between their 
    present day halo mass and their stellar haloes using the \mden{} profiles and 
    scaling relations for massive central galaxies with different $M_{\mathrm{200b}}$ 
    (\rbcg{} and \nbcg{}).

@@

    We perform statistical tests to show that the differences we see in the median 
    \mden{} profiles are significant. 
    We also conduct a variety of tests that verify the robustness of these results 
    against choices of \mtot{} bins, $\lambda$ cut, and redshift range. 
    Please see Appendix~\ref{app:robust} for more details about these tests.

@@

        \item Second, we find that, at fixed \mtot{}, massive central galaxies in 
            more massive dark mater halos display shallower \mden{} profiles that the 
            ones living in less massive haloes. 
            This can be seen from the more flattened inner \mden{} profile and more 
            significant outer stellar halos.

@@

    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in-situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the ``in-situ'' mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive halos host much more prominent outer 
    stellar halo.

    Meanwhile, the uniform slope of the \mden{} profile within 10 kpc is in sharp 
    contrast with the large \textit{intrinsic} scatter in the outskirts. 
    It hints that these two regions are shaped by distinctive processes, and may 
    explain why they depend on environment at different levels.  
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The stochastic nature of the merging process also helps explain the 
    large scatter in the distributions of outer \mden{} profiles. 
    We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
    we show the 3-color images of randomly selected massive central galaxies that 
    have similar \minn{} 
    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
    but different \mtot{}.   
    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.

    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
    (environmental dependence) of structure in massive central galaxies}, which seems 
    to be consistent with the expectation of more frequent (minor) mergers in denser 
    environment. 
    These minor, non-dissipative mergers do not alter the inner \mden{} profiles 
    a lot, but are efficient in depositing stars to the outer envelope
    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})

    The median profiles shown in Fig~\ref{fig:prof_1} are available in Table~1.
%% ------------------------------------------------------------------------------------ %%

@@

\subsubsection{Mass-Size Relation}
    \label{sssec:mass_size}

    Despite numerous attempts, previous studies have failed to clearly 
    demonstrate the existence of an environmental dependence of mass-size relation
    at low-$z$ (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014})

    %Despite being the focus of previous investigations (e.g. \citealt{Shankar2013};
    %\citealt{Leja2013}, \citealt{vdWel2014}), the relation between \mstar{} and 
    %effective radius (or half-light radius; $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$) 
    %has yet to provide clear evidence of environmental dependence of structures of 
    %massive galaxies at low-$z$ (e.g. \citealt{Weinmann2009}, \citealt{Nair2010}, 
    %\citealt{HCompany13}, \citealt{Cerbrian2014}), and sent controversial messages 
    %about the pictures at high-$z$ (e.g. \citealt{MCooper2012}, \citealt{Papovich2012}, 
    %\citealt{Kelkar2015}).

    By using deep HSC images, and by comparing\mden{} profiles directly, 
    we have shown that the structures of massive galaxies do depend on the masses of 
    their host halos (see the left panel of Fig~\ref{fig:scaling_relation}). 
    We now present our results in terms of the more traditional ``mass-size'' relation. 
    For this purpose, we will use \mtot{} as our ``total'' \mstar{} and the radius 
    enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived from the 
    $i$-band curve-of-growth) as our ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction. 
    Our massive galaxies are large enough that we do not need to worry about the 
    effects of seeing.

    Fig~\ref{fig:scaling_relation} shows the \mstar{}-size relations for both samples. 
    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
    \logmtot{}$\geq 11.6$\footnote{We use MCMC and the ensemble sampler 
    \texttt{emcee} (\citealt{Emcee}) with initial guesses are based on maximum 
    likelihood estimates, and we assume reasonable flat priors for parameters.}.
    The best-fit relation for \rbcg{} is:

@@

    \noindent As shown in Fig~\ref{fig:scaling_relation}, the slopes of the \mtot{}-size 
    relations are similar between the two samples, but the normalization of the 
    \mtot{}-size relation is different for \rbcg{} compared to \nbcg{}. 
    This result is robust against the ranges of \mstar{}, also the definitions of 
    ``total'' \mstar{} and  half-light radius\footnote{Using \mstar{} within 120 or 150 
    kpc, or using the $R_{\mathrm{50}}$ derived within these apertures will not change 
    the results.}.

    We qualitatively compare our results with \citealt{HCompany13} (HC13; green solid line) 
    who studied $z\leq 0.09$ central ETGs in  $14\le$ \logmh{} $<15$ halos. 
    HC13 used the group catalog by \citet{Yang2007} to estimate \mhalo{} after empirically 
    convert their \mstar{} from a Kroupa IMF to a Chabrier IMF by applying a constant 
    -0.05 shift (see \citealt{Bernardi2016}).
    They estimated the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We add $+0.1$dex to the HSC13 results to account for the systematic 
    difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
    The mass-size distributions for both \rbcg{} and \nbcg{} galaxies follow the 
    HC13 relation reasonably well (with slightly shallower slopes) even at 
    \logmtot{}$< 11.6$ where our samples start to become incomplete. 
    In contrast to the present study, HC13 finds no halo mass dependence in the 
    mass-size relation for $12.5\le$ \logmh{} $<15.0$ halos.
    A possible explanation for this difference is that the region that strongly depends 
    on halo mass is the low surface brightness outer envelope where the stars are 
    mostly assembled through multiple mergers. 
    This region is difficult to detect on shallow SDSS images, but the much deeper 
    HSC images can provide accurate measurements of total \mstar{} and size.

    In conclusion, we confirm that massive central galaxies at $0.3 < z < 0.5$
    follow \mstar{}-size relations that depend on the masses of their host halos. 
    Central galaxies in denser environment (higher \mhalo{}) have slightly 
    larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
    \mtot{}. 
%% ------------------------------------------------------------------------------------ %%

@@

    Our results suggest that: 
    (1) At fixed \mtot{}, central galaxies in more massive halos tend to have 
    lower fractions of \mstar{} stored in the inner region; 
    (2) For massive galaxies with similar \minn{}, the ones in more massive halos on 
    average have more prominent outer envelopes. 
    The scientific implication of this result is briefly discussed in 
    Section~\ref{sec:discussion}.
%% ------------------------------------------------------------------------------------ %%

>>>>

\title[Structure and Environment of Massive Galaxies]{
       A Detection of the Environmental Dependence of the Stellar Profiles and haloes
       of Massive Central Galaxies}

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    For the first time, we conclusively show that at fixed stellar mass, massive central 
    galaxies display mass density profiles that are not self similar and which 
    present subtle but systematic differences that correlate with \mhalo{}. 
    On average, massive central galaxies in more massive haloes have shallower inner 
    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
    envelopes. 
    These differences translate into a clear environmental dependence of the mass-size 
    relation: central galaxies in more massive haloes have larger $R_{\mathrm{50}}$ 
    at fixed \mtot{}. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    Furthermore, because galaxies in larger haloes have more extended envelopes, 
    the amount of light that is missed will be halo mass dependent. 
    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
    in the amplitude of stellar profiles at 100 kpc. 
    We argue that ``cD'' galaxies represent the tail end of a distribution and 
    are not a distinct class of massive galaxies. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation. 
    \song{This is the abstract of old draft, need some works}

@@

    According to this two-phase formation scenario, the late time growth of massive 
    ETGs is intrinsically tied to the growth of their host dark matter haloes 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive haloes should experience 
    different assembly and should be subject to higher merger rate compared to 
    ETGs with similar \mstar{} that live in less massive dark matter haloes. 
    A natural prediction of this picture is therefore that the structures of 
    massive ETGs should depend on their ``environment''\footnote{There are 
    different definitions of ``environment'' in the literature.  
    In this work, we use ``environment'' and halo mass interchangeably.}.
    For instance, models based on two-phase scenario predict that the well-know 
    stellar mass--effective radius relation for ETGs (\mstar{}--$R_{\rm e}$ relation; 
    e.g., \citealt{Shen2003, Guo2009}) should show environmental dependence: the 
    $R_{\rm e}$ of massive ETGs in more massive haloes should be larger than those 
    in less massive haloes at fixed \mstar{} 
    (e.g. \citealt{Shankar2013, Shankar2014}).
    Yet, solid evidence of this effect at low redshift is still missing 
    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).

@@

    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that the deep, 
    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} massive galaxies 
    at $0.3 < z < 0.5$ out to 100 kpc. 
    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
    and the shapes of the stellar haloes of massive ETGs has a clear \mstar{} 
    dependence. 
    And the fraction of accreted stars residing in the extended envelope increases
    with the total \mstar{} of the galaxy.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          The left panel corresponds to samples matched by ``total'' stellar mass 
          (\mtot{}). 
          The right panel corresponds to samples matched by ``core-mass'' (\minn{}). 
          Orange and red lines correspond to central galaxies living in haloes with 
          \logmh{} $\geq 14.2$. 
          Black and grey correspond to central galaxies living in haloes with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          The brown line in the bottom panels show the relative difference between 
          two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}})$). 
          Errors on the difference between the two profiles is computed via bootstrap 
          too. 
          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial signal. 
          We repeat this process 5000 times.  
          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We also wish to focus on massive galaxies that live at the centers of their own 
    dark matter haloes-- so-called ``central'' galaxies.  
    They are uniquely important to the study of galaxy-halo connection and are known 
    to follow stellar mass--halo mass relation (SHMR; e.g. \citealt{Leauthaud2012, 
    Behroozi2013, Kravtsov2014, Tinker2017}) at high-\mstar{} end with small scatter.
    We utilize the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
    to identify central galaxies.

    Firstly, we select 68 massive central galaxies from the \redm{} clusters 
    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/69 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness of low richness clusters
    at the high end of our redshift window, and the $P_{\mathrm{Cen}}$ limit is 
    selected to exclude low probability candidate of central galaxy. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
    galaxies are the brightest cluster galaxies (BCGs) of clusters with 
    \mhalo{}$>10^{14.2}$~\msun{}.
    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in more massive haloes} as 
    the \rbcg{} sample.

    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
    \citet{Simet2016}. 
    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
    \citet{Diemer2015}. 
    And we exclude all galaxies within a cylinder around each cluster, with the radius
    equal to $R_{\mathrm{200b}}$ and length equal to twice the value of the photometric 
    redshift uncertainty (typically around 0.015 to 0.025). 
    We generally consider this sample as the central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}.
    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
    $0.3 < z < 0.5$. 
    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6). 
    Satellite contamination should be relative low at the high-\mtot{} end
    (e.g. \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
    For instance, the model from \citet{Saito2016} predicts a $\sim 7$\% 
    contamination in the \logmtot{}$>11.6$ sample from satellites from 
    \logmh$<11.4$ haloes.

@@

    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies show 
    intriguing diversity on the \mtot{}-\minn{} plane and in their \mden{} profiles 
    in the outer haloes.  
    In Paper~1, we explore the \mstar{}-dependence of the stellar haloes in massive 
    galaxies, and conclude that the general trends are consistent with the 
    predictions of two-phase formation scenario. 
    In the following sections, we will investigate the relation between their 
    present day halo mass and their stellar haloes using the \mden{} profiles and 
    scaling relations for massive central galaxies with different $M_{\mathrm{200b}}$ 
    (\rbcg{} and \nbcg{}).

@@

    We perform statistical tests to show that the differences we see in the median 
    \mden{} profiles are significant. 
    We also conduct a variety of tests that verify the robustness of these results 
    against choices of \mtot{} bins, $\lambda$ cut, redshift range, and the proxy
    of ``total'' or \textit{in situ} stellar mass. 
    Please see Appendix~\ref{app:robust} for more details about these tests.

@@

        \item Second, we find that, at fixed \mtot{}, massive central galaxies in 
            more massive dark mater haloes display shallower \mden{} profiles that the 
            ones living in less massive haloes. 
            This can be seen from the more flattened inner \mden{} profile and more 
            significant outer stellar haloes.

@@

    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in-situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the ``in-situ'' mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo.

    Meanwhile, the uniform slope of the \mden{} profile within 10 kpc is in sharp 
    contrast with the large \textit{intrinsic} scatter in the outskirts. 
    It hints that these two regions are shaped by distinctive processes, and may 
    explain why they depend on environment at different levels.  
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The scatter of halo assembly process at fixed halo mass and the stochastic 
    nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
    scatter in the outer \mden{} profiles and the diversity seen on the 
    \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).

    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
    (environmental dependence) of \mden{} profiles within 100 kpc in massive central 
    galaxies}. 
    Such dependence seems to be consistent with the expectation of more (minor) 
    mergers in more massive dark matter haloes. 
    Non-dissipative (minor) mergers should not strongly alter the inner \mden{} 
    profiles, but can build up the outer halo efficiently
    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).

@@

    Although the comparisons of \mden{} profiles can reveal the environment dependence 
    directly, it is not straightforward to compare with other observations, model 
    predictions or numerical simulations. 
    In this section, we compare the \rbcg{} and \nbcg{} galaxies on 
    1) the well-know \mstar{}--$R_{\mathrm{e}}$ relation; 
    2) the \mtot{}--\minn{} plane.

%% ------------------------------------------------------------------------------------ %% 
\subsubsection{Mass-Size Relation}
    \label{sssec:mass_size}

    The tight relation between \mstar{} and effective radius (or half-light radius; 
    $R_{\mathrm{e}}$ or $R_{\mathrm{50}}$; e.g. \citealt{Shankar2013, Leja2013, 
    vdWel2014}) is one of the most important scaling relation for ETGs. 
    Despite numerous attempts, previous works failed to demonstrate the impact of 
    environment to the \mstar{}--$R_{\mathrm{e}}$ relation at low-$z$ 
    (e.g. \citealt{Weinmann2009, Nair2010, HCompany13, Cerbrian2014}; 
    but see \citealt{Yoon2017}).

    In the last section, we show that the median \mden{} profiles of massive central 
    galaxies depend on environment. 
    Therefore, we expect to also see difference in the \mstar{}--$R_{\mathrm{e}}$ 
    relations of the \rbcg{} and \nbcg{} samples. 
    For this purpose, we still use \mtot{} as proxy of ``total'' \mstar{}, and adopt 
    the radius enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived 
    from the $i$-band curve-of-growth) as ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction. 
    Massive galaxies from this sample are large enough so we do not need to worry 
    about the effects of seeing.

    Left panel of Fig~\ref{fig:scaling_relation} shows the \mtot{}--$R_{\mathrm{50}}$
    relations for both \rbcg{} (orange--red color) and \nbcg{} (grey--black color). 
    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
    \logmtot{}$\geq 11.6$ using MCMC method with the help from ensemble sampler 
    \texttt{emcee} (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
    likelihood estimates, and we assume reasonable flat priors for parameters.}.
    The best-fit relation for \rbcg{} is:

@@

    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, the slopes 
    of the \mtot{}--$R_{\mathrm{50}}$ relations are similar, but their normalizations 
    show difference between the \rbcg{} and \nbcg{} galaxies. 
    This result is robust against the ranges of \mstar{}, also against the definitions 
    of  ``total'' \mstar{} and half-light radius\footnote{Using \mstar{} within 120 or 
    150 kpc, or using the $R_{\mathrm{50}}$ derived within these apertures will not 
    change the results.}.

    We qualitatively compare our results with \citealt{HCompany13} (HC13; green solid line) 
    who studied $z\leq 0.09$ central ETGs in $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 uses the group catalog by \citet{Yang2007} to estimate \mhalo{} and  
    empirically convert the \mstar{} from a Kroupa IMF to a Chabrier IMF by applying 
    a constant -0.05 shift (see \citealt{Bernardi2016}).
    They estimate the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We add $+0.1$dex to the HSC13 \mstar{} to account for the systematic 
    difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
    The distributions of both \rbcg{} and \nbcg{} galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes) even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies from $12.5\le$ \logmh{} $<15.0$ haloes.
    A possible explanation for this difference is that the region that strongly depends 
    on halo mass is the low surface brightness outer envelope where the stars are 
    mostly assembled through multiple mergers. 
    This region is difficult to detect on shallow SDSS images, but the much deeper 
    HSC images can provide accurate measurements of total \mstar{} and size.

    In conclusion, we confirm that massive central galaxies at $0.3 < z < 0.5$
    follow \mtot{}--$R_{\mathrm{50}}$ relations that show halo mass dependence. 
    At fixed \mtot{}, massive central galaxies in denser environment (higher \mhalo{}) 
    have slightly larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
    \mtot{}. 
%% ------------------------------------------------------------------------------------ %%

@@

    Our results suggest that: 
    (1) At fixed \mtot{}, central galaxies in more massive haloes tend to have 
    lower fractions of \mstar{} stored in the inner region; 
    (2) For massive galaxies with similar \minn{}, the ones in more massive haloes on 
    average have more prominent outer envelopes. 
    The scientific implication of this result is briefly discussed in 
    Section~\ref{sec:discussion}.
%% ------------------------------------------------------------------------------------ %%
